\providecommand{\main}{..}
\documentclass[\main/master.tex]{subfiles}
\begin{document}
\chapter*{Biographical Sketch}
\addcontentsline{toc}{chapter}{Biographical Sketch}  
\hspace{5 mm} Taken from \url{http://www.rochester.edu/Theses/}: ``In one to three paragraphs, provide some basic facts about your scholarly life and career, without including personal data such as birthdate. These include the colleges and universities attended, the major fields of study at each, and the degrees and academic honors awarded. If you have relevant professional experience such as employment in your career field, you may describe it briefly. Follow this with a description of your work at the University of Rochester, including dates of residence, graduate programs pursued, name(s) of advisor(s), and all university appointments (e.g. fellowships, scholarships, research and teaching assistantships or traineeships). Do not include a complete scientific curriculum vitae or professional resume. Do not include future plans or employment. \par
Follow this narrative with a reference list of all works published or in review for publication during your
time at the University, including content or results from the dissertation that have been published in full or in
part. This listing may include publications mentioned on the Contributors and Funding Sources page.'' See the actual guidelines (\url{http://www.rochester.edu/Theses/}) for rules on including previously published articles as chapters in the dissertation. \newline 
An example: \par
[1] Einstein, Albert, ``''\emph{Zur Elektrodynamik bewegter Korper}'' Annalen der Physik 17:891, 1905 \newline

\end{document}